A Dataset of Operator-client Dialogues Aligned with Database Queries for End-to-end Training

### 2016-08-03 paper.tex
final version

\iftrue % FIXME uncomment for final submission
\author{Firstname Lastname \and Firstname Lastname }
\institute{
Insitute\\
\email{anonym@anonymous}
}
\fi

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}
\vspace{-0.50em}
We present a new dataset of human-human task-oriented conversations in the restaurant information domain, suitable for supervised training of autonomous systems. 
We are currently collecting data for the set using crowdsourcing. We have collected 62 dialogues so far; more than 700 dialogues are planned for the final version of the dataset.
% \footnote{We expect to release the set before the camera-ready deadline.}

@@

\section{Conclusion and Future work} \label{sec:conc}
\vspace{-0.50em}
We present a new human-human dialogue dataset with annotation of user intention in the form of operator's database calls.
We also introduced a novel data collection setting which resembles work of operators in call centers and introduces minimum overhead to crowdsourcing workers.
The collected dialogues are published under Creative Commons 4.0 BY-SA license.\footnote{URL will be provided in the camera-ready version of the paper}  % lindat\footnote{todo where}.

@@

% FIXME hidden for anonymised submission
% \vspace{-1.40em}
% \subsubsection*{Acknowledgments}
% We would like to thank Ondřej Dušek for useful comments.
% This research was partly funded by the Ministry of Education, Youth and Sports of the Czech Republic under the grant agreement LK11221, core research funding, grant GAUK 1915/2015, and also partially supported by SVV project number 260 333.
% It used language resources stored and distributed by the LINDAT/CLARIN project of the Ministry of Education, Youth and Sports of the Czech Repub- lic (project LM2015071).
% We gratefully acknowledge the support of NVIDIA Corporation with the donation of the Tesla K40c GPU used for this research.
% Cloud computational resources were provided by the MetaCentrum under the program LM2010005 and the CERIT-SC under the program Center CERIT Scientific Cloud, part of the Operational Program Research and Development for Innovations, Reg.\ no. CZ.1.05/3.2.00/08.0144.

>>>>

% % \iftrue % FIXME uncomment for final submission
% \author{Firstname Lastname \and Firstname Lastname }
% \institute{
% Insitute\\
% \email{anonym@anonymous}
% }
% \fi

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}
\vspace{-0.50em}
We present a new dataset of human-human task-oriented conversations in the restaurant information domain, suitable for supervised training of autonomous systems. 
We are currently collecting data for the set using crowdsourcing. We have collected 62 dialogues so far; more than 700 dialogues are planned for the final version of the dataset.
\footnote{See the dataset at \url{http://hdl.handle.net/11234/1756}.}

@@

\section{Conclusion and Future work} \label{sec:conc}
\vspace{-0.50em}
We present a new human-human dialogue dataset with annotation of user intention in the form of operator's database calls.
We also introduced a novel data collection setting which resembles work of operators in call centers and introduces minimum overhead to crowdsourcing workers.
The collected dialogues are published under Creative Commons 4.0 BY-SA license.

@@

\vspace{-1.40em}
\subsubsection*{Acknowledgments}
We would like to thank Ondřej Dušek for useful comments.
This research was partly funded by the Ministry of Education, Youth and Sports of the Czech Republic under the grant agreement LK11221, core research funding, grant GAUK 1915/2015, and also partially supported by SVV project number 260 333.
It used language resources stored and distributed by the LINDAT/CLARIN project of the Ministry of Education, Youth and Sports of the Czech Repub- lic (project LM2015071).
We gratefully acknowledge the support of NVIDIA Corporation with the donation of the Tesla K40c GPU used for this research.
Cloud computational resources were provided by the MetaCentrum under the program LM2010005 and the CERIT-SC under the program Center CERIT Scientific Cloud, part of the Operational Program Research and Development for Innovations, Reg.\ no. CZ.1.05/3.2.00/08.0144.
